Illuminating a Dark Lens : A Type Ia Supernova \\ Magnified by Galaxy Cluster Abell 2744

### 2015-04-07 snTomas.tex

Another nearby bright galaxy to the East of the SN has a spectroscopic
redshift of $z=1.742$.  This redshift was determined from a spectrum
taken with the G141 grism of the HST WFC3-IR camera, collected as part
of the Grism Lens Amplified Survey from Space (GLASS, PI:Treu,
PID:13459, \citealt{Treu:2015}). \change{As we will see in Sections~\ref{sec:Spectroscopy}
and \ref{sec:PhotometricClassification}, the SN data are inconsistent
with that redshift, meaning that this spatially nearby galaxy is a background
object and therefore has no impact on the SN magnification.}

@@

For Type Ia SNe, the SALT2 model has two additional parameters that
control the shape ($x_1$) and color ($c$) of the light curve.  We use
conservative priors here, defined to encompass a range of Type Ia SN
shapes and colors that is broader than typically allowed in
cosmological analyses \citep[see
e.g.,][]{Kessler:2009b,Sullivan:2011,Rest:2014}. For $x_1$ the prior is
a bifurcated Gaussian distribution with mean $\bar{x}_1=0$, dispersion
$\sigma_{x_1}^+={0.9}$ and $\sigma_{x_1}^-={-1.5}$.  The prior for the
color parameter $c$ has $\bar{c}=0.0$, $\sigma_c^-=0.08$, and
$\sigma_c^+=0.54$, using the same distribution as for $x_1$.  The $c$ parameter in SALT2 combines intrinsic SN
color and extinction due to dust, so the large red tail of this
distribution allows for the possibility of several magnitudes
of dust extinction along the \tomas\ line of sight.

@@

\change{
In general, free-form methods tend to explore the model parameter
space more fully than parametric methods.  This is reflected in the
size of the error-bars in Figure~\ref{fig:lensingtest}.  For example,
GRALE(Williams?), which has the largest, and possibly the most realistic
uncertainties is able to account for mass sheet degeneracy by
introducing a free parameter in the reconstruction that represents an
arbitrarily positioned mass sheet, with normalization to be chosen by
the genetic algorithm.  More complex degeneracies are also accounted
for in GRALE(Williams?) through the use of basis
functions \citep{Liesenborgs:2006,Liesenborgs:2007,Mohammed:2014} }

>>>>

Another nearby bright galaxy to the East of the SN has a spectroscopic
redshift of $z=1.742$.  This redshift was determined from a spectrum
taken with the G141 grism of the HST WFC3-IR camera, collected as part
of the Grism Lens Amplified Survey from Space (GLASS, PI:Treu,
PID:13459, \citealt{Treu:2015}). \change{As we will see in Sections~\ref{sec:Spectroscopy}
and \ref{sec:PhotometricClassification}, the SN data are inconsistent
with that redshift, meaning that this is a background
object and therefore has no impact on the SN magnification.}

@@

For Type Ia SNe, the SALT2 model has two additional parameters that
control the shape ($x_1$) and color ($c$) of the light curve.  We use
conservative priors here, defined to encompass a range of Type Ia SN
shapes and colors that is broader than typically allowed in
cosmological analyses \citep[see
e.g.,][]{Kessler:2009b,Sullivan:2011,Rest:2014}. For $x_1$ the prior
is a bifurcated Gaussian distribution with mean $\bar{x}_1=0$,
dispersion $\sigma_{x_1}^+={0.9}$ and $\sigma_{x_1}^-={-1.5}$.  The
bifurcated Gaussian prior for the color parameter $c$ has
$\bar{c}=0.0$, $\sigma_c^-=0.08$, and $\sigma_c^+=0.54$.  The $c$
parameter in SALT2 combines intrinsic SN color and extinction due to
dust, so the large red tail of this distribution allows for the
possibility of several magnitudes of dust extinction along the \tomas\
line of sight.

@@

\change{
In general, free-form methods tend to explore the model parameter
space more fully than parametric methods.  This is reflected in the
size of the error-bars in Figure~\ref{fig:lensingtest}.  For example,
the Williams model (using GRALE), which has the largest, and possibly the
most realistic uncertainties is able to account for mass sheet
degeneracy by introducing a free parameter in the reconstruction that
represents an arbitrarily positioned mass sheet, with normalization to
be chosen by the genetic algorithm.  More complex degeneracies are
also accounted for in this model through the use of basis
functions \citep{Liesenborgs:2006,Liesenborgs:2007,Mohammed:2014} }
